
\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=0.65in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\pagestyle{empty}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
{\LARGE \textbf{GANESH KUMAR}}\\
\vspace{2mm}
Software Engineer | Full-Stack Developer\\
\vspace{2mm}
+91-9122855361 \quad|\quad
\href{mailto:gannu9122@gmail.com}{gannu9122@gmail.com}\\
\href{https://www.linkedin.com/in/ganesh-kumar-2a46b82a4}{LinkedIn}
\end{center}

\section*{Education}
\textbf{Dronacharya Group of Institutions}\\
B.Tech in Computer Science \& Engineering \hfill 2023--2027

\section*{Technical Skills}
\textbf{Languages:} C++, Java, JavaScript, Python (Basic)\\
\textbf{Frontend:} HTML, CSS, React.js, Tailwind CSS, Bootstrap\\
\textbf{Backend:} Node.js, Express.js, REST APIs\\
\textbf{Databases:} MongoDB, MySQL (SQL)\\
\textbf{Tools:} Git, VS Code, Postman\\
\textbf{Core CS:} DSA, OOP, DBMS, Operating Systems, Computer Networks

\section*{Projects}

\textbf{AI Plagiarism Detection System}\\
\textit{React.js | Node.js | Express.js | Python | MongoDB}
\begin{itemize}[leftmargin=*]
\item Built an AI-powered plagiarism detection platform supporting PDF document uploads.
\item Implemented TF-IDF and Cosine Similarity to compare documents.
\item Developed secure authentication using JWT and MongoDB for report storage.
\item Designed responsive UI and REST APIs for document processing.
\end{itemize}

\textbf{Real-Time Collaborative Code Editor}\\
\textit{React.js | Node.js | Socket.IO | Monaco Editor}
\begin{itemize}[leftmargin=*]
\item Developed a collaborative editor with real-time code synchronization.
\item Implemented Socket.IO rooms for multi-user collaboration.
\item Added authentication, room management and live collaboration.
\item Integrated Monaco Editor for a professional coding experience.
\end{itemize}

\textbf{AI Interview Preparation Platform}\\
\textit{React.js | Node.js | Express.js | MongoDB}
\begin{itemize}[leftmargin=*]
\item Developed an AI-based mock interview platform.
\item Implemented resume upload and interview history.
\item Built secure REST APIs with JWT authentication.
\item Created responsive dashboards and analytics views.
\end{itemize}

\section*{Achievements}
\begin{itemize}[leftmargin=*]
\item Strong foundation in Full-Stack Web Development using the MERN stack.
\item Solving Data Structures and Algorithms using C++.
\item Passionate about scalable backend systems and AI-powered applications.
\end{itemize}

\end{document}
